---
title: "MNI152 to MNI305 to tkrRAS"
format: html
editor: visual
jupyter: python3
---

## Configuration

```{r, setup, include = FALSE}
knitr::opts_knit$set(root.dir = 'G:/My Drive/Residency/Research/Lab - Damisah/Project - Sleep')
```

```{r}
library(tidyverse)
library(threeBrain)
library(raveio)
```

## Parameters

```{r}
elec_file <- 'Cache/Subject01/S01_electrodes_MNI152.csv'

output_path <- 'Cache/Subject01/S01_electrodes_tkrRAS.csv'
```

## Import N27 brain template

threeBrain only comes with one brain template, the N27 from Freesurfer. You can download a few other templates from the threeBrain GitHub but otherwise you will need to add them manually into the folder specified by default_template_directory().

Download templates if you have not done so:

```{r}
#download_template_subject('N27')
#download_template_subject('fsaverage')
#download_template_subject('cvs_avg35_inMNI152')

#default_template_directory()
#set_default_template('N27')
```

Initialize template brain:

```{r}
template_path <- file.path(default_template_directory(),
                           'N27')

# freesurfer_brain2() will eventually be deprecated by threeBrain()
brain <- freesurfer_brain2(
  fs_subject_folder = template_path,
  subject_name = 'N27', 
  surface_types = c('pial',
                    'white',
                    'smoothwm'),
  atlas_types = c('aparc.DKTatlas+aseg')
  )
```

## Convert coordinates

threeBrain plots electrodes in tkRAS space (proprietary to Freesurfer), so we need to transform the LeGUI output from its MNI152 space into MNI305, and then into tkrRAS.

```{r}
elec_info <- read.csv(elec_file)
mni152 <- elec_info[, c('MNI152_x', 
                        'MNI152_y', 
                        'MNI152_z')]

## Convert from MNI152 to MNI305 by specifying the 
## MNI305-to-MNI152 transform and doing the reverse:
mni152 <- rbind(t(as.matrix(mni152)), 1)
mni305 <- solve(threeBrain:::MNI305_to_MNI152) %*% mni152

## Convert from MNI305 to tkrRAS by specifying the 
## tkrRAS-to-MNI305 transform and doing the reverse:
## (note that the order of matrix multiplication matters!)
tkrRAS <- brain$Torig %*% solve(brain$Norig) %*% solve(brain$xfm) %*% mni305

## Generate final electrode coordinates
tkrRAS <- data.frame(
  Coord_x = tkrRAS[1, ],
  Coord_y = tkrRAS[2, ],
  Coord_z = tkrRAS[3, ],
  MNI305_x = mni305[1, ],
  MNI305_y = mni305[2, ],
  MNI305_z = mni305[3, ]
)

elec_info <- cbind(elec_info, tkrRAS)
```

## Export

Save for use in threeBrain/RAVE and MRIcroGL

```{r}
elec_info <- elec_info[, c('Electrode', 'Coord_x',
                           'Coord_y', 'Coord_z',
                           'Label', 'MNI305_x', 
                           'MNI305_y', 'MNI305_z')]

write.csv(elec_info, 
          output_path, 
          row.names = FALSE)
```
