---
title: "wat"
format: html
editor: visual
---

## Configuration

```{r, setup, include = FALSE}
knitr::opts_knit$set(root.dir = 'G:/My Drive/Residency/Research/Lab - Damisah/Project - Sleep/Revisions')
```

```{r}
library(tidyverse)
library(cowplot)
```

## Parameters

If you get errors when trying to display the plots (especially anything related to "scales_add_default()"), it is because the RDS files have to have been exported from environments using the same exact version of ggplot2 that you are using when you load the RDS file back into the R environment. So if you used ggplot2 version 3.4.2 to export the ggplot into an RDS file, then you have to have ggplot2 version 3.4.2 in your environment when you load the RDS file again, or it will not display properly.

```{r}
# hypno <- readRDS('Cache/S01_Feb02_hypnogram.RDS')
# scalp <- readRDS('Cache/S01_Feb02_scalp_spectrogram.RDS')
# iceeg <- readRDS('Cache/S01_Feb02_iceeg_spectrogram.RDS')
# swa <- readRDS('Cache/S01_Feb02_SWA.RDS')
# #sw <- readRDS('Cache/S01_Feb02_SW.RDS')
# cspikes <- readRDS('Cache/S01_Feb02_color_spikes.RDS')
# pca <- readRDS('Cache/S01_Feb02_pca_spikes.RDS')
# output_path <- 'Results/S01_Feb02_overview_plot.svg'
# hypno_legend_path <- 'Results/S01_Feb02_hypno_legend.svg'
# scalp_legend_path <- 'Results/S01_Feb02_scalp_legend.svg'
# iceeg_legend_path <- 'Results/S01_Feb02_iceeg_legend.svg'
# swa_legend_path <- 'Results/S01_Feb02_swa_legend.svg'
# #sw_legend_path <- 'Results/S01_Feb02_sw_legend.svg'
# cspikes_legend_path <- 'Results/S01_Feb02_cspikes_legend.svg'
# pca_legend_path <- 'Results/S01_Feb02_pca_legend.svg'
# 
# hypno <- readRDS('Cache/S05_Jul11_hypnogram.RDS')
# scalp <- readRDS('Cache/S05_Jul11_scalp_spectrogram.RDS')
# iceeg <- readRDS('Cache/S05_Jul11_iceeg_spectrogram.RDS')
# swa <- readRDS('Cache/S05_Jul11_SWA.RDS')
# #sw <- readRDS('Cache/S05_Jul11_SW.RDS')
# cspikes <- readRDS('Cache/S05_Jul11_color_spikes.RDS')
# pca <- readRDS('Cache/S05_Jul11_pca_spikes.RDS')
# output_path <- 'Results/S05_Jul11_overview_plot.svg'
# hypno_legend_path <- 'Results/S05_Jul11_hypno_legend.svg'
# scalp_legend_path <- 'Results/S05_Jul11_scalp_legend.svg'
# iceeg_legend_path <- 'Results/S05_Jul11_iceeg_legend.svg'
# swa_legend_path <- 'Results/S05_Jul11_swa_legend.svg'
# #sw_legend_path <- 'Results/S05_Jul11_sw_legend.svg'
# cspikes_legend_path <- 'Results/S05_Jul11_cspikes_legend.svg'
# pca_legend_path <- 'Results/S05_Jul11_pca_legend.svg'

hypno <- readRDS('Cache/S05_Jul13_hypnogram.RDS')
scalp <- readRDS('Cache/S05_Jul13_scalp_spectrogram.RDS')
iceeg <- readRDS('Cache/S05_Jul13_iceeg_spectrogram.RDS')
swa <- readRDS('Cache/S05_Jul13_SWA.RDS')
#sw <- readRDS('Cache/S05_Jul13_SW.RDS')
cspikes <- readRDS('Cache/S05_Jul13_color_spikes.RDS')
pca <- readRDS('Cache/S05_Jul13_pca_spikes.RDS')
output_path <- 'Results/S05_Jul13_overview_plot.svg'
hypno_legend_path <- 'Results/S05_Jul13_hypno_legend.svg'
scalp_legend_path <- 'Results/S05_Jul13_scalp_legend.svg'
iceeg_legend_path <- 'Results/S05_Jul13_iceeg_legend.svg'
swa_legend_path <- 'Results/S05_Jul13_swa_legend.svg'
#sw_legend_path <- 'Results/S05_Jul13_sw_legend.svg'
cspikes_legend_path <- 'Results/S05_Jul13_cspikes_legend.svg'
pca_legend_path <- 'Results/S05_Jul13_pca_legend.svg'
```

### Main Plot

```{r}
hypno_2 <- hypno + theme(legend.position = 'none', 
                         plot.margin = unit(c(0, 0, 0, 0), 'cm'))

scalp_2 <- scalp + theme(legend.position = 'none', 
                         plot.margin = unit(c(0, 0, 0, 0), 'cm'))

iceeg_2 <- iceeg + theme(legend.position = 'none', 
                         plot.margin = unit(c(0, 0, 0, 0), 'cm'))

swa_2 <- swa + theme(legend.position = 'none', 
                     plot.margin = unit(c(0, 0, 0, 0), 'cm'))

#sw_2 <- sw + theme(legend.position = 'none', 
#                   plot.margin = unit(c(0, 0, 0, 0), 'cm'))

cspikes_2 <- cspikes + theme(legend.position = 'none', 
                             plot.margin = unit(c(0, 0, 0, 0), 'cm'))

pca_2 <- pca + theme(legend.position = 'none', 
                     plot.margin = unit(c(0, 0, 0, 0), 'cm'))
```

### Export

```{r}
# # Original with detected SW
# plot_grid(hypno_2, scalp_2, iceeg_2, swa_2, sw_2, cspikes_2, pca_2, 
#           ncol = 1, align = 'hv', axis = 'lr',
#           rel_heights = c(0.75, 1, 1, 0.5, 0.5, 1.5, 0.4))

# ggsave(file = output_path, width = 7, height = 5, 
#        dpi = 300, limitsize = FALSE)

# Revision without detected SW
plot_grid(hypno_2, scalp_2, iceeg_2, swa_2, cspikes_2, pca_2, 
          ncol = 1, align = 'hv', axis = 'lr',
          rel_heights = c(0.75, 1, 1, 0.75, 1.5, 0.5))

ggsave(file = output_path, width = 7, height = 4.5, 
       dpi = 300, limitsize = FALSE)
```

### Legends

```{r}
legend <- cowplot::get_legend(hypno)
legend_plot <- ggdraw() + draw_plot(legend)
ggsave(filename = hypno_legend_path, plot = legend_plot, device = 'svg')

legend <- cowplot::get_legend(scalp)
legend_plot <- ggdraw() + draw_plot(legend)
ggsave(filename = scalp_legend_path, plot = legend_plot, device = 'svg')

legend <- cowplot::get_legend(iceeg)
legend_plot <- ggdraw() + draw_plot(legend)
ggsave(filename = iceeg_legend_path, plot = legend_plot, device = 'svg')

legend <- cowplot::get_legend(swa)
legend_plot <- ggdraw() + draw_plot(legend)
ggsave(filename = swa_legend_path, plot = legend_plot, device = 'svg')

#legend <- cowplot::get_legend(sw)
#legend_plot <- ggdraw() + draw_plot(legend)
#ggsave(filename = sw_legend_path, plot = legend_plot, device = 'svg')

legend <- cowplot::get_legend(cspikes)
legend_plot <- ggdraw() + draw_plot(legend)
ggsave(filename = cspikes_legend_path, plot = legend_plot, device = 'svg')

legend <- cowplot::get_legend(pca)
legend_plot <- ggdraw() + draw_plot(legend)
ggsave(filename = pca_legend_path, plot = legend_plot, device = 'svg')
```
